A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-14 EvoPar2017/paper.Rnw
Adds the entropy graph

@@

>>>>

# Entropy data
new.data <- read.csv("../data/nodio-2016-3-17-0_by_exp.csv")
new.data <- new.data[new.data$actualPUTs>=16,] # Filters short experiments (uses old data)
new.experiment.data <- data.frame( Experiment=rep("17-0", length(new.data$IPs)),                   
                                  milliseconds=as.integer(new.data$milliseconds),
                                  IPs=as.integer(new.data$IPs),
                                  actualIPs=as.integer(new.data$actualIPs),
                                  PUTs=as.integer(new.data$PUTs),
                                  actualPUTs=as.integer(new.data$actualPUTs),
                                  PUTsIP=as.integer(new.data$PUTs)/as.integer(new.data$IPs),
                                  entropy=as.numeric(new.data$entropy),
                                  cacheEntropy=as.numeric(new.data$cacheEntropy)
                                  )

@@

In order to have enough data to perform more analysis on it, a new
experiment was performed along several days with, eventually, several
hundreds of persons participating on it. It was announced by several
popular Twitter figures and found its way into Reddit. The number of
PUTs per minute are shown in \ref{fig:minute}. Sudden peaks in them
are due to new announcements. Please check also the dot color, which
corresponds to the {\em ratio} or, as indicated above, the actual
number of contributing PUTs, those that have not been discarded due to
repeated sending by clients or (briefly) belonging to the previous
instance of the experiment. It reveals that, in some cases where the
amount of PUTs really increases, they are actually not contributing so
much, while light dots, corresponding to a ration close to 1, usually
stay in the lowest part of the graphic.

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing.
%
\begin{figure}[ht!b]
\centering
<<entropy, cache=FALSE,echo=FALSE>>=
max <- max(new.experiment.data$IPs)
exp.palette <- colorRampPalette(brewer.pal(12,"Paired"))
ggplot(data=new.experiment.data)+geom_point(aes(x=entropy,y=milliseconds,size=PUTs,color=IPs))+scale_x_log10()+scale_y_log10()+scale_color_gradient(limits=c(1,max),low='red')
@ %def entropy data
%
\caption{Entropy of the user contribution vs. time to solution in the
  volunteer computing experiment. \label{fig:entropy}}
\end{figure}

### 2016-11-14 EvoPar2017/paper.tex
Adds the entropy graph

>>>>

In order to have enough data to perform more analysis on it, a new
experiment was performed along several days with, eventually, several
hundreds of persons participating on it. It was announced by several
popular Twitter figures and found its way into Reddit. The number of
PUTs per minute are shown in \ref{fig:minute}. Sudden peaks in them
are due to new announcements. Please check also the dot color, which
corresponds to the {\em ratio} or, as indicated above, the actual
number of contributing PUTs, those that have not been discarded due to
repeated sending by clients or (briefly) belonging to the previous
instance of the experiment. It reveals that, in some cases where the
amount of PUTs really increases, they are actually not contributing so
much, while light dots, corresponding to a ration close to 1, usually
stay in the lowest part of the graphic.

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing.
%
\begin{figure}[ht!b]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/entropy-1}

\end{knitrout}
%
\caption{Entropy of the user contribution vs. time to solution in the
  volunteer computing experiment. \label{fig:entropy}}
\end{figure}
